Slitasje og kjørespor

### 2022-12-14 DRAFT_slitasjeOgKjørespor.Rmd
cache

#### Nature type mapping
This indicator uses the dataset `Naturtyper etter Miljødirektoratets Instruks`, which can be found [here](https://kartkatalog.geonorge.no/metadata/naturtyper-miljoedirektoratets-instruks/eb48dd19-03da-41e1-afd9-7ebc3079265c).
See [here](#naturtype) for a detailed description of tha dataset.

```{r, eval=T}

@@

>>>>

#### Nature type mapping
This indicator uses the dataset `Naturtyper etter Miljødirektoratets Instruks`, which can be found [here](https://kartkatalog.geonorge.no/metadata/naturtyper-miljoedirektoratets-instruks/eb48dd19-03da-41e1-afd9-7ebc3079265c).
See [here](#naturtype) for a detailed description of the dataset.

Importing the full dataset can be done like this 
```{r, eval=T}

@@

Export subsetted data set
```{r}
saveRDS(naturetypes, "P:/41201785_okologisk_tilstand_2022_2023/data/rds/naturtyper.rds")
```
